\documentclass[../Thesis_AHoecherl.tex]{subfiles}

\begin{document}
\section{Margining}\label{Margining}

In the context of derivatives, margining refers to the process of posting and receiving collateral in the form of cash or securities to reduce the counterparty credit risk associated with the derivatives.

Counterparty credit risk refers to the risk of a default of the counterparty of a derivative. Derivatives are contracts between two institutions which give raise to future cash flows dependent of the performance of its underlying. These future cash flows are at risk if the counterparty defaults during the lifetime of the derivative. 

Over the past decades several measures were established in the derivatives markets to mitigate counterparty credit risk.

The most impactful measure is close-out netting. Close-out netting is a contractual agreement of two counterparties how their bilateral derivative contracts have to be settled if one of the counterparties defaults. With close-out netting, in case one of the two counterparties defaults all derivatives which are yet to mature are immediately closed out based on their current market value. The market values of the individual derivatives are summed up and the netted amount needs to be paid by whichever party is trailing across the portfolio. In case of a default this close-out netting procedure takes priority over all other claims of creditors against the defaulted counterparty. 

Close-out netting has two major advantages. 
First, the non-defaulting counterparty only suffers a counterparty credit loss, if it is ahead across the entire portfolio of currently running derivatives with the defaulted party. Just having a positive market value on a few derivatives does not necessarily result in a counterparty credit loss. Secondly, the immediate close-out of the open derivatives of the defaulted counterparty greatly facilitates unwinding its portfolio. 

A disadvantage of close-out netting is, that it may proof difficult to find an objective market value of the derivatives that have to be closed out - especially in a stressed market environment, which is likely to be present if e.g. a large investment bank defaults. The contractual obligation to perform close-out netting is agreed upon in a master agreement, which was introduced to the derivatives market by \gls{ISDA} in 1985. Currently, close out netting is in effect for almost all traded derivatives and it will implicitly always be assumed to be in effect throughout this thesis. More details on close-out netting may be found in \cite[Chapter~5]{gregory2015xva}.

The second most effective measure in mitigating counterparty credit risk is the exchange of variation margin. If the obligation to post variation margin is agreed as part of a master agreement, the accrued mark-to-market of the derivative portfolio has to be collateralized by the trailing counterparty. This measure effectively resets counterparty credit risk to zero for both parties every time a variation margin payment is made or the exchanged variation margin is adjusted to the current market value of the portfolio. The exchange of variation margin was common but not a given in the inter-bank market before the financial crisis of 2008. After the crisis it has become commonplace in the interbank market and recently has even been mandated by regulators\footnote{In the European Union the exchange of Variation Margin for inter bank bilateral \gls{OTC} derivatives is compulsory since September of 2016 for large banks or March of 2017 for smaller banks.}. Non-financial counterparties oftentimes do not collateralize their derivatives since they are not mandated to do so, shy away from the operational burden and have a harder time funding the significant amount of cash necessary to cover the current mark-to-market value of their entire derivatives portfolio. Collateralizing a derivatives portfolio not only significantly reduces \gls{CCR} but also significantly alters how the remaining \gls{CCR} behaves. The \gls{CCR} of a collateralized portfolio may rather be driven by the terms of the collateral support annex or residual phenomenon such as collateral spikes than by the underlying instruments \cite{andersen2017does}. 

As a final measure, initial margin can be exchanged. Historically, initial margin was a collateral amount that was calculated and exchanged once at the inception of a new derivative and held until maturity - hence the name \emph{initial} margin. One common formulation used w.r.t. initial margin, which has also found its way into regulatory documents (e.g. \cite[Article 52.16]{CRE52}) is that initial margin is collateral, that - in contrast to variation margin - is not based on the \gls{MtM} of a portfolio or derivative. 

The idea behind initial margin is that it secures the counterparties against losses that can incur between the last time variation margin has been exchanged prior to a default until the original position has been restored. This time period is referred to as the margin period of risk and this time period results as the sum of
\begin{enumerate}
    \item The contractually agreed regular frequency of variation margin exchanges
    \item The time it takes from a counterparty not complying with a margin call to ascertain that the counterparty has indeed defaulted
    \item The necessary time to reopen the defaulted derivatives with new counterparties to rehedge the bank and thereby restoring the risk profile held prior to the default of the counterparty.\label{step3}
\end{enumerate}
Initial margin should cover the gap between the \gls{MtM} of the derivatives with the defaulted counterparty when variation margin was last exchanged to the price for which the derivatives are reopened in step \ref{step3} under the assumption that the market has moved unfavorably during the margin period of risk(\gls{MPoR}). In the context of CCR, \emph{unfavorable} means that the banks position would have increased in value throughout the margin period of risk and therefore the market price for which the bank repurchases the derivatives is higher than the value at which variation margin was exchanged last.

The use of these different measures to mitigate counterparty credit risk between two parties and their parametrization is set in the credit support annex (\gls{CSA}). 
A credit support annex is a legal document arranged between derivative counterparties that, among others, regulates the exchange of margin and the proceedings in case of a default of one of the counterparties.
Generally, negotiated CSAs are based on some template provided by \gls{ISDA} and therefore have a homogeneous structure but contract parameters have to be agreed bilaterally and can show some variety.

A range of parameters of a \gls{CSA} is of special interest within the scope of this thesis and therefore warrant a more detailed inspection. 
In the following we only focus on bilateral contracts regarding uncleared derivatives, i.e. contracts that do not involve a \gls{CCP} as a counterparty.

\begin{description}
    \item[Collateralization with variation margin]
    The counterparties decide whether the portfolio has to be collateralized with variation margin.
    If so, the calculated variation margin is the sum of the \gls{PV} of all trades within the portfolio.
    The counterparties need to agree on a common valuation of a portfolio. This can be a complex process, especially if differences in pricing need to be resolved.
    Once a calculated variation margin has been determined it depends on the minimum transfer amount, margin call frequency and variation margin threshold how much of the calculated variation margin is actually exchanged. 
    \item[Variation margin threshold]
    If a variation margin threshold is in place, no variation margin is exchanged before the absolute calculated variation margin does exceed this threshold.
    The purpose of the threshold is mainly to reduce operational efforts related to very small derivative portfolios. In line with focus on operational impact and in contrast to the initial margin threshold, the calculated variation margin amount is usually exchanged in full once the threshold has been exceeded.
    Variation margin thresholds are banned by the regulator for any portfolio for which bilateral initial margin needs to be exchanged \cite[Requirement 2.1]{BCBS_MarginRequirements}. 
    \item[Collateralization with initial margin]
    In a bilateral contract, the counterparties need to agree whether they collateralize their portfolio with initial margin and how they will calculate the initial margin.
    If initial margin should be exchanged it can be calculated with an internal model or a standardized model. It is also possible to calculate the \gls{IM} of parts of the portfolio under the internal model while others are calculated under the standardized model.
    Bilateral initial margin models are further discussed in section \ref{Bilateral initial margin}.
    \item[Initial margin threshold]
    If an initial margin threshold is in place and the calculated initial margin does not exceed this threshold, no initial margin is exchanged.
    Additionally, the regulator allows that even if the threshold is exceeded it may be deducted from the calculated initial margin resulting in the exchanged initial margin being the calculated \gls{IM} minus the \gls{IM} threshold.
    The regulator allows an \gls{IM} threshold of up to 50Mn USD or EUR \cite[Requirement 2.2]{BCBS_MarginRequirements} which is quite a considerable amount in comparison to the calculated \gls{IM} of average derivative portfolios \cite{ISDAMarginSurvey}.
    \item[Minimum transfer amount]
    If a minimum transfer amount is in place, margin is only exchanged if the margin amount that would need to be exchanged based on current calculations differs by more than the minimum transfer amount from the margin that has already been exchanged.
    Details on how exactly the \gls{MTA} applies may vary but within the scope of this thesis we assume that a common \gls{MTA} may be in place for both initial and variation margin amounts. If bilateral initial margin is exchanged the minimum transfer amount may not exceed 500000EUR according to European regulation \cite[Requirement 2.3]{BCBS_MarginRequirements}.  
    \item[Margin frequency]
    The margin frequency determines with which frequency margins need to be recalculated and - assuming that the \gls{MTA} is exceeded - adjusted. Margin frequencies may differ between \gls{VM} and \gls{IM} calculations of the same \gls{CSA} and are subject to regulation. The regulator e.g. expects that the margin frequency for variation margin is daily \cite[Requirement 3.14]{BCBS_MarginRequirements}.
\end{description}

Having a \gls{CSA} in place is a prerequisite for two financial or non-financial counterparties to enter any derivative contract with each other.

A more comprehensive introduction to counterparty credit risk and its reduction through netting and margining may be found in chapters four through six of \cite{gregory2015xva}.

\subsection{Market structure and associated margining approaches}\label{sec:Market strucutre and associated margining approaches}

The derivative market is divided into exchange traded derivatives, cleared \gls{OTC} derivatives and uncleared bilateral derivatives. Uncleared bilateral derivatives can either be uncollateralized, collateralized with \gls{VM} or collateralized with \gls{IM} and \gls{VM}. Below, these five counterparty relations are briefly introduced. They are ordered w.r.t. their associated counterparty credit risk.

\begin{description}
    \item[Uncollateralized bilateral derivatives\label{itm:Uncollateralized bilateral derivatives}] 
    Derivatives are arranged between two counterparties without involvement of a third party. No collateral is exchanged at any point, only the contractual cashflows of the derivatives are exchanged. The \gls{CCR} is very high as the entire \gls{MtM} of the portfolio is at risk. Since no margin is posted at all, the \gls{MPoR} is the maturity of the traded derivatives and can therefore easily eclipse multiple years. \gls{IM} posted, \gls{IM} received and \gls{VM} are zero at all times.
    \item[Bilateral derivatives collateralized with VM\label{itm:Bilateral derivatives collateralized with VM}] 
    The \gls{CCR} is still significant. When the counterparty defaults the bank can suffer unmitigated losses for a couple of days until it can rebuild its position. The \gls{MtM} of the portfolio is collateralized with \gls{VM}. \gls{VM} exchange is subject to contract parameters such as the threshold, minimum transfer amount or the exchange frequency. Values of these parameters impact how well \gls{CCR} is mitigated.
    \item[Bilateral derivatives collateralized with \gls{VM} and \gls{IM}\label{itm:Bilateral derivatives collateralized with VM and IM}] 
    Counterparty credit risk is low. Only in edge cases is it possible that the counterparties credit losses surpass the available collateral. An \gls{MPoR} of at least 10 days is mandated by the regulator \cite[Requirement 3.1]{BCBS_MarginRequirements}. The \gls{IM} is calculated with an internal or standardized bilateral initial margin model. Posted and received \gls{IM} are recalculated daily. \gls{VM} exchange obeys the same mechanics as for \ref{itm:Bilateral derivatives collateralized with VM}.
    \item[Cleared \gls{OTC} derivatives\label{itm:Cleared OTC derivatives}] 
    Derivatives are initially arranged bilaterally between two counterparties and then cleared by a \gls{CCP}. The \gls{CCP} takes over positions in case of a default of either party mitigating any \gls{CCR} in the traditional sense. The bank has no direct counterparty credit risk. It may however suffer losses to its clearing fund contribution if another Member of the \gls{CCP} defaults. The \gls{MPoR} is mandated by the regulator to be five days \cite[Article 26]{CCP_margining_regulation}. The initial margin that is posted by the bank to the \gls{CCP} is calculated by the \gls{CCP} with his proprietary internal initial margin model. In line with the assumption that the \gls{CCP} can not default, the \gls{CCP} does not post \gls{IM} to its clearing members. Therefore, the \gls{IM} received from the perspective of the bank is always zero. The daily \gls{PnL} of the portfolio is exchanged as \gls{VM} between the \gls{CCP} and the Bank. 
    \item[Exchange traded derivatives\label{itm:Exchange traded derivatives}] 
    Banks enter positions in exchange traded derivatives listed by a \gls{CCP}. Positions are matched by the \gls{CCP} and the counterparties of a transaction remain anonymous to each other. Associated \gls{CCR} and margining is largely the same as for \ref{itm:Cleared OTC derivatives} but the \gls{MPoR} is generally below five days since it is assumed that positions in exchange traded derivatives can be closed faster than in cleared \gls{OTC} derivatives. The used internal initial margin model may differ e.g. since the regulator requires coverage of a 99\% quantile instead of the 99.5\% mandated for cleared \gls{OTC} derivatives \cite[Article 24]{CCP_margining_regulation}.
\end{description}

According to \cite[Figure~3.2]{gregory2015xva} based on notional 9\% of derivatives are exchange traded, 55\% are cleared \gls{OTC} derivatives and 36\% are uncleared \gls{OTC} derivatives. It has to be noted that these figures are from 2014 and it can be assumed, that the fraction of cleared \gls{OTC} derivatives has increased since then at the expense of the fraction of uncleared \gls{OTC} derivatives. The reason for this is, that regulators have incentivized or even mandated the clearing of simpler \gls{OTC} derivatives over the course of the last years. In connection with this development the large \glspl{CCP} such as Eurex or the LCH have extended the product range for which they offer \gls{OTC} clearing in recent years.

Within the scope of this thesis we will only investigate the allocation of the first three cases listed above, i.e. uncleared derivatives.


\end{document}